Replikationskrise, Open Science und p-hacking: Die Studierenden

### 2019-09-16 manuscript/manuscript.Rmd
update link to supplements

```{r global variables, include=FALSE}
fnt <- "Arial"
lbreak <- ""
tab.counter <- 0
rounding_number <- 1 # for percentages
online.suppl <- "placeholder"
link <- glue("[{online.suppl}]({online.suppl})")
tables <- list()
```

>>>>

```{r global variables, include=FALSE}
fnt <- "Arial"
lbreak <- ""
tab.counter <- 0
rounding_number <- 1 # for percentages
online.suppl <- "https://osf.io/br2zf/"
link <- glue("[{online.suppl}]({online.suppl})")
tables <- list()
```
